Towards semantic-rich word embeddings

### 2019-04-05 paper/main.tex
Improve keyword and context descriptions

\section{Our method}
\subsection{Keyword embedding}
\label{sec:kw_embed}
\textit{Keyword} is a sequence of words that lets us disambiguate between different meanings of the same ambiguous word, e.g. \textit{tree (forest)} that represents a tree as a plant and \textit{tree (structure)} which represents tree as a mathematical structure.

@@

\subsection{Context embedding}
\label{sec:ctx_embed}
\textit{Context} is a sequence of words that contains an ambiguous word within, usually in the middle.
It is parametrized by \textbf{context length \(l\)}, which specifies how many of words from both side of the ambiguous word in question were taken into consideration.

>>>>

\section{Our method}
\subsection{Keyword embedding}
\label{sec:kw_embed}
\textit{Keyword} is a sequence of words that is composed of the ambigous word and words describing its specific meaning, e.g. \textit{tree (forest)} that represents tree as a plant (ambiguous word: \textit{tree}, meaning: \textit{forest}) and \textit{tree (structure)} which represents tree as a mathematical structure (ambiguous word: \textit{tree}, meaning: \textit{structure}).

@@

\subsection{Context embedding}
\label{sec:ctx_embed}
\textit{Context} is a sequence of words, extracted from some text, which contains an ambiguous word and words surrounding it in text.
It is parametrized by \textbf{context length \(l\)}, which specifies how many words from both sides of the ambiguous word are taken into consideration.
